Machine learning assessment
========================================================
## Summary
- Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively.
- The data for this project come from this source: [http://groupware.les.inf.puc-rio.br/har].
- In this paper, I predict the test setdata from the train data using regression tree method and use 5-fold cross-validation to calculate the accurancy.


## clean the data
### After downing the data, I clean the data as follows:
1. load the data
```{r cache=TRUE}
setwd("C:/Users/Administrator/Desktop/machine learning")
options(stringsAsFactors=F)
train<-read.csv("pml-training.csv")
test<-read.csv("pml-testing.csv")
```
2. Give two datasets as same names:
```{r cache=TRUE}
names(train)->names(test)
```
3. Create a label to show whether it is a train data or test data
```{r cache=TRUE}
rep(0,dim(train)[1])->lab
train1<-data.frame(train,labs=lab)
rep(NA,dim(test)[1])->lab
test1<-data.frame(test[,1:159],classe=lab,labs=test[,160])
```
4. Delete the variables which are not numberic or integer
```{r cache=TRUE}
as.character(test1[,160])->test1[,160]
set<-rbind(test1,train1)
attach(set)
train_data<-data.frame(ID=X,
                  user_name=factor(user_name),num_window=num_window,
                  roll_belt=roll_belt,pitch_belt=pitch_belt,
                  yaw_belt=yaw_belt,
                  total_accel_belt=total_accel_belt,
                  gyros_belt_x=gyros_belt_x,gyros_belt_y=gyros_belt_y,
                  gyros_belt_z=gyros_belt_z,accel_belt_x=accel_belt_x,
                  accel_belt_y=accel_belt_y,accel_belt_z=accel_belt_z,
                  magnet_belt_x=magnet_belt_x,magnet_belt_y=magnet_belt_y,
                  magnet_belt_z=magnet_belt_z,roll_arm=roll_arm,
                  pitch_arm=pitch_arm,yaw_arm=yaw_arm,
                  total_accel_arm=total_accel_arm,
                  gyros_arm_x=gyros_arm_x,gyros_arm_y=gyros_arm_y,
                  gyros_arm_z=gyros_arm_z,accel_arm_x=accel_arm_x,
                  accel_arm_y=accel_arm_y,accel_arm_z=accel_arm_z,
                  magnet_arm_x=magnet_arm_x,magnet_arm_y=magnet_arm_y,
                  magnet_arm_z=magnet_arm_z,roll_dumbbell=roll_dumbbell,
                  pitch_dumbbell=pitch_dumbbell,
                  yaw_dumbbell=yaw_dumbbell,total_accel_dumbbell=total_accel_dumbbell,
                  gyros_dumbbell_x=gyros_dumbbell_x,gyros_dumbbell_y=gyros_dumbbell_y,
                  gyros_dumbbell_z=gyros_dumbbell_z,accel_dumbbell_x=accel_dumbbell_x,
                  accel_dumbbell_y=accel_dumbbell_y,accel_dumbbell_z=accel_dumbbell_z,
                  magnet_dumbbell_x=magnet_dumbbell_x,magnet_dumbbell_y=magnet_dumbbell_y,
                  magnet_dumbbell_z=magnet_dumbbell_z,roll_forearm=roll_forearm,
                  pitch_forearm=pitch_forearm,yaw_forearm=yaw_forearm,
                  total_accel_forearm=total_accel_forearm,
                  gyros_forearm_x=gyros_forearm_x,gyros_forearm_y=gyros_forearm_y,
                  gyros_forearm_z=gyros_forearm_z,accel_forearm_x=accel_forearm_x,
                  accel_forearm_y=accel_forearm_y,accel_forearm_z=accel_forearm_z,
                  magnet_forearm_x=magnet_forearm_x,magnet_forearm_y=magnet_forearm_y,
                  magnet_forearm_z=magnet_forearm_z,
                  classe=factor(classe),labs=labs )
detach(set)
```
### It's not a good method to clean the data,I know there are some good ways to solve it so, please tell me in the feedback.

4. Save the data and clean the Gobal Enviroment
```{r cache=TRUE}
save(train_data, file='train_data.RData')
rm(list=ls())
gc()

```

## Build the model
1. Load the data
```{r cache=TRUE}
library(caret)
load("train_data.RData")
train<-train_data[train_data$labs==0,]
test<-train_data[!train_data$labs==0,]
```
2. split the data in 5 parts
```{r cache=TRUE}
ids <- train$ID
set.seed(114)
ids <- split(ids, sample(length(ids)) %% 5)
sapply(ids,length)
```
3. 5-fold cv: using classification tree
```{r cache=TRUE}
Acc<-0
for ( i in 1:5 ){
training<-train[-unlist(ids[i]),c(-1,-57)]
testing<-train[unlist(ids[i]),c(-1,-57)]
modelFit1<-train(classe~.,data=training,method="rpart")
cM<-confusionMatrix(testing$classe,predict(modelFit1,testing))
cM$overall[i]->Acc[i]
}
```
### After calculating the 5-fold cv,overall accurancy is shown.
```{r cache=TRUE}
mean(Acc)
```
### It's not really impressive...
## final model
1. fit the model
```{r cache=TRUE}
rm(list=ls())
gc()
load("train_data.RData")
train<-train_data[train_data$labs==0,]
test<-train_data[!train_data$labs==0,]
final_train<-train[,c(-1,-57)]
finalModel<-train(classe~.,data=final_train,method="rpart")
final_test<-test[,c(-1,-57)]
answer<-predict(finalModel,final_test)
confusionMatrix(final_train$classe,predict(finalModel,final_train))
```
2. predict the test dataset
```{r cache=TRUE}
answer<-as.character(answer)
answer
```
3. Write the txt flies:
```{r eval=FALSE}
  pml_write_files = function(x){
    n = length(x)
    for(i in 1:n){
      filename = paste0("problem_id_",i,".txt")
      write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
    }
  }
  pml_write_files(answer)
```